---
title: "Data Products Course Project"
author: "John Fortin"
date: "8/12/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("titanic_data_load_only.R")
train_ds = load_titanic_data()
library(ggplot2)
library(randomForest)
```

##

#### Analyzing the Titanic Data Set
<p>An interesting way to explore and gain skill in Data Science is to explore the various datasets and competitions hosted at http://kaggle.com.  

<p>One dataset frequently used for analysis is the Titanic Survivor dataset used in the practice competition called "Titanic: Machine Learning from Disaster"

<p>We will be looking at this dataset and its characteristics during this presentation.  

<p>The following page has the basic summary of the data for Passenger Class, Age, Sex, Family Size, Child, and Fare

----

#### Titanic Training Data Set Summary
```{r}
summary(train_ds[,c("Pclass", "Age", "Sex", 
                    "FsizeD", "Child", "Fare")])
```
* FsizeD: Family Size 
* Pclass: Passenger Class

----

#### Graphical Analysis
<p> A great way to get insight into a dataset is to graph various relationships between the parameters.  For instance we might be interested in how a passengers age or fare impacted survival on the Titanic.

```{r, fig.height=1.5, fig.width=7}
qplot(train_ds$PassengerId, 
          train_ds$Age,
          color=train_ds$Survived,
          xlab = "Passenger Id",
          ylab = "Age"
          )
qplot(train_ds$PassengerId, 
          train_ds$Fare,
          color=train_ds$Survived,
          xlab = "Passenger Id",
          ylab = "Fare"
          )
```

----
<p>The next stage for a data analysis would be to create prediction models for the data.

<p>An interactive prediction model can be found at: https://fortinj66.shinyapps.io/data_products_course_project/
